%%%% english mou
{\bf
  {\LARGE
    \centerline{Memorandum of Understanding}
  }
  {\Large
    \centerline{between}
    \centerline{\institution}
    \centerline{and}
    \centerline{the LAGO Collaboration}
    \vspace*{0.2cm}
    \centerline{\datesignen}
  }
}

\section{Introduction}

This Memorandum of Understanding describes the commitments by members of
\institution~to the LAGO Project. The purpose of this project is the design,
installation, commissioning and operation of the LAGO project, an extended
Astroparticle Observatory at global scale.
%Latin American Giant Observatory. 
It is mainly oriented to basic research on three branches of Astroparticle
physics: the Extreme Universe, Space Weather phenomena, and Atmospheric
Radiation at ground level.

The LAGO detection network consists in single or small arrays of particle
detectors at ground level, spanning over different sites located at
significantly different latitudes (currently from Mexico up to the Antarctic
region) and different altitudes (from sea level up to more than 5000 meters
over sea level), covering a huge range of geomagnetic rigidity cut-offs and
atmospheric absorption/reaction levels. 

The LAGO Project is operated by the LAGO Collaboration, a non-centralized
distributed collaborative network omposed by several institutions from
different countries.

This Memorandum of Understanding describes the long term contributions of
\institution~to design, construction and operation of the LAGO Project. It is
understood that the anticipated contributions of \institution~may be modified
or that additional responsibilities may be added to those described here. 

This Memorandum of Understanding is made among \institution, hereby
represented by \instrep, the LAGO \country~representative, hereby represented
by \countryrep, and the LAGO Collaboration, hereby represented by the LAGO
Principal Investigator \lagopi, hereinafter jointly referred to as ``the
Parties'', or separately as a ``party''. It does not constitute a legal
contractual obligation for either of the parties. It reflects an arrangement
that is currently satisfactory to the parties involved.  The parties agree to
negotiate additional amendments to this memorandum as required to meet the
evolving requirements of \institution~and/or the LAGO Project.

\section{Personnel}

\subsection{List of Scientific Personnel}

Participating scientists including technical staff, postdocs and students
committed to the LAGO Project during the full project period and the fraction
of their time dedicated to the project are expected to be:

\input{local/t1-personal.tex}

According to the LAGO membership policies, all the personnel listed,
hereinafter referred to as ``the members of the LAGO Collaboration associated
to \institution'' or shortly ``the LAGO members of \institution'', will
participate in at least one of the Working Groups of the LAGO Project. So then,
the LAGO members of \institution~will be part of the LAGO list of authors. 

The Institution Representative (see subsection \ref{iren}) of \institution~will
communicate personnel incorporations, separations or changes to this list to
the \country~Representative in a monthly basis.

\subsection{Institution Representative\label{iren}}

\instrep~is the present representative of \institution~at the LAGO
Collaboration, and was elected by the LAGO members of \institution~according to
the policies of the LAGO Collaboration. \instrep~will act as the main contact
between the LAGO members of \institution~and the LAGO Collaboration through the
LAGO \country~Representative. 

\section{Design, Fabrication, Installation and Operation Responsibilities}

\subsection{Design and Fabrication Responsibilities - Construction Period}

\subsubsection{Description of Items Provided by \institution}

\institution~agrees on a best efforts basis to provide the following
components, materials and services:

\input{local/t2-aporte.tex}

These items belong to \institution, but will be used exclusively for the
operations of \institution~within the LAGO project. Since all these items will
be used only by members of \institution~in their facilities or operated sites,
\institution~will not claim to the LAGO Collaboration for the deterioration or
damage of these items.

\subsubsection{Description of Items Provided by the LAGO Collaboration}

The LAGO Collaboration agrees to provide to \institution~the following
components, materials, software and services:

\input{local/t3-lago.tex}

\institution~agrees to receive these items, which belong to the LAGO
Collaboration, under the figure of {\it{commodatum}} and will be used for its
specific usage as part of the LAGO Project by the \institution~members of the
LAGO Collaboration. These items must be returned to the LAGO Collaboration in
essence and without deterioration or in kind, after previous agreement between
the parties, by solicitude of a party or by the end of this arrangement.

\subsubsection{Installation, Commissioning and Operation}

\institution\ will participate in the installation, commissioning and operation
of the contributed items and will have personnel at the site as listed:

\input{local/a1-commitment.tex}

\subsubsection{Data Access}

All the data produced by the LAGO Project belong to the LAGO Collaboration,
both the data collected by the LAGO detectors (``measured data'') and the
simulated data associated with the Project (``synthetic data''), hereinafter
jointly referred to as ``the LAGO data''. In spite of that all the authoring
rights on the data sets will be acknowledge.

All the LAGO members of \institution~have full access to the full data sets,
and to the official software tools developed to analyze these data. The parties
agree to provide the necessary infrastructure or methods to guarantee the
access to the LAGO data in a regular manner. Data produced by the LAGO
detectors associated to \institution~will be treated according to the LAGO data
policies established by the Scientific Committee of the LAGO Collaboration. 

\subsection{Reporting}

\institution~will report all LAGO Project related expenditures and associated
technical progress on a quarterly basis to the Country Representative of
\country. All status reports will be assembled and made public to the LAGO
Collaboration by the Coordination Committee of the LAGO Project.

\section{Signatories}

The following persons concur in the terms of this Memorandum of 
Understanding.  These terms will be updated as appropriate in Amendments to 
this Memorandum.

\input{footer.tex}
