\documentclass[12pt,a4paper]{article}
\usepackage{graphicx}
\usepackage[left=2.5cm,top=2.5cm,right=2cm,bottom=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[spanish,english]{babel}
%\usepackage[spanish,english,portuguese]{babel}
\usepackage[bitstream-charter]{mathdesign}

\newif\ifes
\newif\ifen
\newif\ifpt
\newif\ifintro


\introfalse % true if you want the introductory page
% \introtrue
\begin{document}

\include{local/header}

\ifintro
\begin{center}
{\Large\bf 
  the Latin American Giant Observatory (LAGO) Collaboration\\
  \vspace*{0.7cm}
  \datesign
}
\end{center}
\vspace*{1.5cm}

The attached Memoranda of Understanding describe the commitments by members of
the signing institutions to the LAGO Project. The purpose of the LAGO project
is the design, installation, commissioning and operation of the Latin American Giant
Observatory, an extended cosmic ray observatory composed by single or small
arrays of particle detectors at global scale. Its main scientific objectives
are oriented to basic astroparticle research on three branches: the Extreme Universe, Space
Weather phenomena, and Atmospheric Radiation at ground level.

Through these documents, the members listed in the attached Memoranda of
Understanding constitute the LAGO Collaboration and manifest their commitment
to build and operate the LAGO project, the analysis of its data,
and the funding of these activities through the relevant funding agencies.

\vspace*{1cm}\begin{center}\noindent\rule{0.9\textwidth}{0.4pt}\end{center}\vspace*{1cm}

\begin{center}
{\Large\bf 
  la Colaboración Latin American Giant Observatory (LAGO)\\
  \vspace*{0.7cm}
  \datesign
}
\end{center}
\vspace*{1.5cm}

Los Memorándums de Entendimiento adjuntos describen los compromisos de los
miembros de las instituciones participantes en el Proyecto LAGO. El objetivo
del proyecto LAGO es el diseño, la construcción, la puesta en servicio y la
operación del Observatorio Gigante Latinoamericano (LAGO, por sus siglas en
inglés), un observatorio de rayos cósmicos extendido compuesto compuesto por
detectores de partículas individuales o formando pequeños arreglos a escala
global. Sus principales objetivos científicos se orientan a la investigación
básica en Astropartículas en tres ramas: el Universo Extremo, fenómenos de
Meteorología y Climatología Espacial, y Radiación Atmosférica a nivel del
suelo. 

Por medio de estos documentos, los miembros que se detallan en los Memorándums
de Entendimiento anexos consituyen la Colaboración LAGO y expresan su
compromiso a la construcción y operación del proyecto LAGO, el análisis de sus
datos y la financiación de estas actividades a través de las agencias de
financiamiento relevantes.

%% FALTA EN PORTUGUES

\fi

% Spanish
\selectlanguage{spanish}
\estrue
\enfalse
\ptfalse
\def \country{\countryes}
\setcounter{secnumdepth}{10}
\input{mou-es}

% English
\newpage
\selectlanguage{english}
\esfalse
\entrue
\ptfalse
\def \country{\countryen}
\setcounter{section}{0}
\input{mou-en}

% Portuguese
% \nepage
% \selectlanguage{portuguese}
% \esfalse
% \enfalse
% \pttrue
% \def \country{\countrypt}
% \setcounter{section}{0}
% \input{mou-pt}
\end{document}
